Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-14 paper/paper.tex
hscc17

A discrete-time linear system is said to be Bounded-Input and Bounded-Output
(BIBO) stable if and only if every pole of its transfer function lies inside
the unit circle.  Analyzing Eq.~\eqref{eq:outputfunctions}, the following
lemma states necessary conditions for BIBO stability of the closed-loop system
in Figure~\ref{fig:sampledsystem}, since the exogenous signals $R(z)$,
$\nu_{1}$, and $\nu_{2}$ are bounded.

\begin{mylemma}{\cite{Bessa16,fadali}}
\label{lemma:eq_int_stab} 
%
A feedback hybrid control system as given in Figure~\ref{fig:sampledsystem},
with a FWL implementation of the digital controller $\hat{C}(z) =
\frac{\mathit{FWL}[N_{C}(z)]}{\mathit{FWL}[D_{C}(z)]}$ and uncertain
discrete model of the plant $\vec{\hat{G}}=\vec{G}+\Delta_p \vec{G}+\Delta_q
\vec{G} \Rightarrow \hat{G}(z)=\frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$, is
BIBO-stable if and only if:
%
\begin{itemize}
\item  the roots of characteristic polynomial $S(z)$ are inside the open unit circle, where $S(z)$ is:
\begin{equation}
\label{eq:internal_stab_lemma}
S(z)=\mathit{FWL}[N_{C}(z)]\hat{N}_{G}(z)+\mathit{FWL}[D_{C}(z)]\hat{D}_{G}(z);
\end{equation}
\item the direct loop product $\frac{\mathit{FWL}[N_{C}(z)]}{\mathit{FWL}[D_{C}(z)]}\cdot \frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$ has no pole-zero cancellation on or outside the unit circle.
\end{itemize}
\end{mylemma}

>>>>

It is known that a discrete-time linear system is said to be Bounded-Input and Bounded-Output
(BIBO) stable if and only if every pole of its transfer function lies inside
the unit circle \cite{Astrom08}.  Analyzing Eq.~\eqref{eq:outputfunctions}, the following
proposition states necessary conditions for BIBO stability of the closed-loop system
in Figure~\ref{fig:sampledsystem}, since the exogenous signals $R(z)$,
$\nu_{1}$, and $\nu_{2}$ are bounded.

\red{[it's not a lemma, since it is not later used to prove a theorem. state it as a proposition (theorem would be a bit of an over-statement)]}

\begin{mylemma}{\cite{Bessa16,fadali}}
\label{lemma:eq_int_stab} 
%
A feedback closed-loop control system as given in Figure~\ref{fig:sampledsystem},
with a FWL implementation of the digital controller $\hat{C}(z) =
\frac{\mathit{FWL}[N_{C}(z)]}{\mathit{FWL}[D_{C}(z)]}$ and uncertain
discrete model of the plant $\vec{\hat{G}}=\vec{G}+\Delta_p \vec{G}+\Delta_q
\vec{G}$, namely \red{[utter confusion between transfer functions and coefficients - you're next taking the ratio between two vectors of coefficient, which magically now are also a function of the z variable! WTF!  \ldots]} $\hat{G}(z)=\frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$, is
BIBO-stable if and only if:
%
\begin{itemize}
\item  the roots of characteristic polynomial $S(z)$ are inside the open unit circle, where $S(z)$ is:
\begin{equation}
\label{eq:internal_stab_lemma}
S(z)=\mathit{FWL}[N_{C}(z)]\hat{N}_{G}(z)+\mathit{FWL}[D_{C}(z)]\hat{D}_{G}(z);
\end{equation}
\item the direct loop product $\frac{\mathit{FWL}[N_{C}(z)]}{\mathit{FWL}[D_{C}(z)]}\cdot \frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$ has no pole-zero cancellation on or outside the unit circle.
\end{itemize}
\end{mylemma}
